Main Analyses

### 2016-02-18 Rmd/main-analysis.Rmd
Redid Carbon stocks to correct fact that I was using veg biomass, not C, adding below ground, and re-ran through most of main-analysis up until first plots, using updated model to account for faulty grid ordering.

```{r, warning=FALSE, message=FALSE}
library(agroEcoTradeoff)
library(readxl)
library(gdalUtils)
library(gisutils)
setwd("~/Dropbox/publications/zambiaToff/private/zambiaToff/")
p_root <- getwd()
p_demand <- fp(p_root, "external/input_devel/demand/")
p_mod <- fp(p_root, "agroEcoTradeoff")
p_moddat <- fp(p_mod, "external/data/ZA")
p_figures <- full_path(p_root, "paper/figures/")
p_roads <- fp(p_root, "external/input_devel/roads")
p_roads2 <- paste0("/Users/lestes/Dropbox/data/zari/infrastructure/zambia/", 
                   "rda_dump/Final Shape files RDA/")
p_out <- fp(p_mod, "external/output")
```

@@

# rasters
mzsoyr <- stack(list(mztor, soytor * 2))
mzsoyr <- calc(mzsoyr, sum)
plot(mzsoyr)
# plot(roads)

# Plot
i1 <- rbind(mzto$impacts, soyto$impacts)
crops <- c("maize", "soy", "maize/soy")
# plot(1:10, pch = 20, cex = 4, col = "gold2")
# plot(mzsoyr, col = c("grey", "goldenrod", "green4", "orange"))
imp_plot2(mzsoyr, i1, p_figures, "ideal_yield2", "", crops, TRUE, 
         c("gold2", "green3", "orange"))

@@

### Best Areas for Other Three Factors
```{r, eval = FALSE}
basedt <- soyto$inputs$mask
ybl <- list(yb1 <- c(1, 1))
step <- 0.05
cnames <- c("C", "BD", "COST")
ps <- round(do.call(rbind, pareto_steps(cnames, step)), 2); head(ps)
Yv = "conv_area"; Cv = "tot_C"; BDv = "int_mean"; COSTv = "mu_cost"
Yst = sum; Cst = sum; BDst = mean; COSTst = mean
crops <- list("maize", "soy", c("maize", "soy"))
croplnms <- list("maize", "soy", "both")
# lapply(crops, function(x) targ[x])
# lapply(crops, function(x) g[x])
cbdc <- lapply(crops, function(x) {
  a <- Sys.time()
  print(paste("Starting run for", x, "at", a))
  otab <- pareto(cnames, step = step, prod_targ = targ[x], 
                 yblist = ybl, currprodmod = g[x], input_key = "ZA", 
                 Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
                 Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
                 silent = FALSE, ncl = 7)
  load(fp(p_out, "bcode.rda"))
  heatr <- heat(fp(p_out, bcode), basedt, todisk = TRUE) 
  print(Sys.time() - a)
  c("bcode" = bcode, otab, "heat" = heatr)
})
names(cbdc) <- croplnms

# check for datasets where certain weights were removed from contention
clength <- t(sapply(cbdc, function(x) c(nrow(x$params), nrow(x$optitab))))
cbdcmz <- heat2(cbdc$maize, fp(p_out, cbdc$maize$bcode), basedt, todisk = TRUE)
cbdc$maize$heat <- cbdcmz

# load(fp(p_out, "ZA_20160213_172518_13217_37779/impacts_tab.rda"))
# save(cbdc, file = fp(p_out, "results.rda"))
# par(mfrow = c(2, 2), mar = c(0, 0, 0, 4))
# plot(cbdc$both$heat, axes = FALSE, box = FALSE)
# plot(cbdc$maize$heat, axes = FALSE, box = FALSE)
# plot(cbdc$soy$heat, axes = FALSE, box = FALSE)
# a <- Sys.time()
# print(a)
# cbdc_mz <- pareto(cnames, step = step, prod_targ = targ["maize"], 
#                   yblist = ybl, currprodmod = g["maize"], input_key = "ZA", 
#                   Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
#                   Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
#                   silent = FALSE, ncl = 8)
# Sys.time() - a
# load(fp(p_out, "bcode.rda"))
# bcodes <- bcode
# a <- Sys.time()
# cbdc_soy <- pareto(cnames, step = step, prod_targ = targ["soy"], 
#                    yblist = ybl, currprodmod = g["soy"], input_key = "ZA", 
#                    Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
#                    Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
#                    silent = FALSE, ncl = 8)
# Sys.time() - a
# load(fp(p_out, "bcode.rda"))
# bcodes[2] <- bcode
# implist <- list(cbdc_mz, cbdc_soy)
# names(implist) <- bcodes

# tstmp <- function() {
#   paste0(gsub(" ", "", gsub(":|-", "", as.character(Sys.time()))))
# }
# save(implist, file = fp(p_out, paste0("imptabs_", tstmp(), ".rda")))
# load(fp(p_out, "imptabs_20160212165418.rda"))
# implist

# Create overlap maps
# CRSobj <- CRS(soyto$inputs$sp$crs)
# cbdc_mz_ht <- heat_func(fp(p_out, names(implist)[1]), basedt) 
# cbdc_soy_ht <- heat_func(fp(p_out, names(implist)[2]), basedt) 
# plot(cbdc_soy_ht + cbdc_mz_ht)
# plot(cbdc_soy_ht)
# Might need to run it for both crops simultaneously

# Do RGB plot comparing overlaps between two

@@

### Conservation interests versus agricultural interests
```{r, eval = FALSE}
ybl <- list(yb1 <- c(1, 1))
step <- 0.02
cnames <- c("Y", "COST")
ps <- round(do.call(rbind, pareto_steps(cnames, step)), 2)
# ps[which(rowSums(ps[, c(1, 3)]) == 0), ]

ycost <- lapply(crops, function(x) {
  a <- Sys.time()
  print(paste("Starting run for", x, "at", a))
  otab <- pareto(cnames, step = step, prod_targ = targ[x], 
                  yblist = ybl, currprodmod = g[x], input_key = "ZA", 
                  Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
                  Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
                  silent = FALSE, ncl = 7)
  load(fp(p_out, "bcode.rda"))
  heatr <- heat(fp(p_out, bcode), basedt, todisk = TRUE) 
  print(Sys.time() - a)
  c("bcode" = bcode, otab, "heat" = heatr)
})
names(ycost) <- croplnms

clength <- t(sapply(ycost, function(x) c(nrow(x$params), nrow(x$optitab))))

cnames <- c("C", "BD")
bdc <- lapply(crops, function(x) {
  a <- Sys.time()
  print(paste("Starting run for", x, "at", a))
  otab <- pareto(cnames, step = step, prod_targ = targ[x], 
                  yblist = ybl, currprodmod = g[x], input_key = "ZA", 
                  Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
                  Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
                  silent = FALSE, ncl = 7)
  load(fp(p_out, "bcode.rda"))
  heatr <- heat(fp(p_out, bcode), basedt, todisk = TRUE) 
  print(Sys.time() - a)
  c("bcode" = bcode, otab, "heat" = heatr)
})
names(bdc) <- croplnms
# bdc3 <- c(bdc, bdc2)  # vestiges to show I forgot to do maize soy case
# bdc <- bdc3

bdcfix <- lapply(bdc, function(x) {  # x <- bdc$maize
  if(nrow(x$params) > nrow(x$optitab)) {
    print(paste("fixing heat map for", x$bcode))
    heatfix <- heat2(x, fp(p_out, x$bcode), basedt, todisk = TRUE)
  } else {
    heatfix <- NULL
  }
  heatfix
})
for(i in 1:length(bdc)) bdc[[i]]$heat <- bdcfix[[i]]

save(cbdc, ycost, bdc, file = fp(p_out, "mainresults1302.rda"))
```

# ran because of fail on iteration for both (croplnms not properly compiled)
# bnames <- c("ZA_20160213_231906_17404_28678", "ZA_20160213_234959_17404_39818")
# ybdc <- lapply(bnames, function(x) {
#   bpath <- fp(p_out, x)
#   load(fp(bpath, "optitab.rda"))
#   load(fp(bpath, "parms.rda"))
#   list("bcode" = x, "optitab" = optimal, "params" = parms)
# })
# names(ybdc) <- croplnms[1:2]

# heat maps
ybdcheat <- lapply(ybdc, function(x) {  # x <- bdc$maize
  print(paste("N params =", nrow(x$params), ": N optimal =",  nrow(x$optitab)))
  heatfix <- heat2(x, fp(p_out, x$bcode), basedt, todisk = TRUE, 
                   overwrite = TRUE)
  heatfix
})
for(i in 1:length(ybdc)) ybdc[[i]]$heat <- ybdcheat[[i]]

plot(ybdc$maize$heat)
par(mfrow = c(1, 2))
plot(ycost$maize$heat)
plot(ycost$soy$heat)
plot(ycost$both$heat)
plot(bdc$both$heat)

@@

>>>>

```{r, warning=FALSE, message=FALSE}
library(agroEcoTradeoff)
library(readxl)
library(gdalUtils)
library(gisutils)

setwd("~/Dropbox/publications/zambiaToff/private/zambiaToff/")
p_root <- getwd()
p_demand <- fp(p_root, "external/input_devel/demand/")
p_mod <- fp(p_root, "agroEcoTradeoff")
p_moddat <- fp(p_mod, "external/data/ZA")
p_figures <- full_path(p_root, "paper/figures/")
p_roads <- fp(p_root, "external/input_devel/roads")
p_roads2 <- paste0("/Users/lestes/Dropbox/data/zari/infrastructure/zambia/", 
                   "rda_dump/Final Shape files RDA/")
p_out <- fp(p_mod, "external/output")
```

@@

# rasters
mzsoyr <- stack(list(mztor, soytor * 2))
mzsoyr <- calc(mzsoyr, sum)
# plot(mzsoyr)
# plot(roads)

# Plot
i1 <- rbind(mzto$impacts, soyto$impacts)
crops <- c("maize", "soy", "maize/soy")
# plot(1:10, pch = 20, cex = 4, col = "gold2")
# plot(mzsoyr, col = c("grey", "goldenrod", "green4", "orange"))
imp_plot2(mzsoyr, i1, p_figures, "ideal_yield", "", crops, 1, TRUE, 
         c("gold2", "green3", "orange"))

basedt <- soyto$inputs$mask
```

### Best Areas for Other Three Factors

Switch off for now
```{r, eval = FALSE}
# ybl <- list(yb1 <- c(1, 1))
# step <- 0.05
# cnames <- c("C", "BD", "COST")
# ps <- round(do.call(rbind, pareto_steps(cnames, step)), 2); head(ps)
# Yv = "conv_area"; Cv = "tot_C"; #BDv = "int_prior"; COSTv = "mu_cost"
# BDv = c(Yv, "int_prior"); COSTv = c(Yv, "mu_cost")
# wmu <- function(x, na.rm = na.rm) {
#   weighted.mean(x = x[, 2], w = x[, 1], na.rm = na.rm)
# }
# # Yst = sum; Cst = sum; BDst = mean; COSTst = mean
# Yst = sum; Cst = sum; BDst = wmu; COSTst = wmu
# 
# # crops <- list("maize", "soy", c("maize", "soy"))
# crops <- list(c("maize", "soy"))
# # croplnms <- list("maize", "soy", "both")
# croplnms <- list("both")
# # lapply(crops, function(x) targ[x])
# # lapply(crops, function(x) g[x])
# cbdc <- lapply(crops, function(x) {
#   a <- Sys.time()
#   print(paste("Starting run for", x, "at", a))
#   otab <- pareto(cnames, step = step, prod_targ = targ[x], 
#                  yblist = ybl, currprodmod = g[x], input_key = "ZA", 
#                  Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
#                  Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
#                  silent = FALSE, ncl = 7)
#   load(fp(p_out, "bcode.rda"))
#   heatr <- heat(fp(p_out, bcode), basedt, todisk = TRUE) 
#   print(Sys.time() - a)
#   c("bcode" = bcode, otab, "heat" = heatr)
# })
# names(cbdc) <- croplnms
# 
# # cbdc <- lapply("ZA_20160215_071436_1558_16149", function(x) {
# #   bpath <- fp(p_out, x)
# #   load(fp(bpath, "impacts_tab.rda"))
# #   inlist <- lapply(unique(outtab$iter), function(x) {
# #     outtab[outtab$iter == x, ]
# #   })
# #   # load(fp(bpath, "optitab.rda"))
# #   optimal <- batch_stat(inlist, Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, 
# #                         Yst = Yst, Cst = Cst, BDst = BDst, COSTst = COSTst)
# #   save(optimal, file = fp(bpath, "optitab.rda"))
# #   load(fp(bpath, "parms.rda"))
# #   heatr <- heat2(fp(p_out, x), basedt, todisk = TRUE, overwrite = TRUE) 
# #   list("bcode" = x, "optimal" = optimal, "params" = parms, "heat" = heatr)
# # })
# # names(cbdc) <- croplnms
# 
# # check for datasets where certain weights were removed from contention
# # clength <- t(sapply(cbdc, function(x) c(nrow(x$params), nrow(x$optitab))))
# # cbdcmz <- heat2(cbdc$maize, fp(p_out, cbdc$maize$bcode), basedt, todisk = TRUE)
# # cbdc$maize$heat <- cbdcmz

@@

### Conservation interests versus agricultural interests
```{r, eval = FALSE}
ybl <- list(yb1 <- c(1, 1))
step <- 0.02
cnames <- c("Y", "COST")
ps <- round(do.call(rbind, pareto_steps(cnames, step)), 2)
# ps[which(rowSums(ps[, c(1, 3)]) == 0), ]
Yv = "conv_area"; Cv = "tot_C"
BDv = c(Yv, "int_prior"); COSTv = c(Yv, "mu_cost")
wmu <- function(x, na.rm = na.rm) {
  weighted.mean(x = x[, 2], w = x[, 1], na.rm = na.rm)
}
Yst = sum; Cst = sum; BDst = wmu; COSTst = wmu

crops <- list(c("maize", "soy"))
croplnms <- list("both")

ycost <- lapply(crops, function(x) {
  a <- Sys.time()
  print(paste("Starting run for", x, "at", a))
  otab <- pareto(cnames, step = step, prod_targ = targ[x], 
                  yblist = ybl, currprodmod = g[x], input_key = "ZA", 
                  Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
                  Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
                  silent = FALSE, ncl = 7)
  load(fp(p_out, "bcode.rda"))
  heatr <- heat2(fp(p_out, bcode), basedt, todisk = TRUE) 
  print(Sys.time() - a)
  c("bcode" = bcode, otab, "heat" = heatr)
})
names(ycost) <- croplnms
# plot(ycost$both$optitab$Y, ycost$both$optitab$COST)

# fix because ran with heat2 not yet adjusted for improperly ordered csv files
ycostfix <- lapply(ycost, function(x) {  # x <- ycost$both
  if(nrow(x$params) > nrow(x$optitab)) {
    print(paste("fixing heat map for", x$bcode))
    heatfix <- heat2(fp(p_out, x$bcode), basedt, TRUE, TRUE)
  } else {
    heatfix <- NULL
  }
  heatfix
})
for(i in 1:length(ycost)) ycost[[i]]$heat <- ycostfix[[i]]

# ycost <- lapply("ZA_20160215_072118_1558_04246", function(x) {
#   bpath <- fp(p_out, x)
#   load(fp(bpath, "impacts_tab.rda"))
#   inlist <- lapply(unique(outtab$iter), function(x) {
#     outtab[outtab$iter == x, ]
#   })
#   optimal <- batch_stat(inlist, Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, 
#                         Yst = Yst, Cst = Cst, BDst = BDst, COSTst = COSTst)
#   save(optimal, file = fp(bpath, "optitab.rda"))
#   load(fp(bpath, "parms.rda"))
#   heatr <- heat2(fp(p_out, x), basedt, todisk = TRUE, overwrite = TRUE) 
#   list("bcode" = x, "optimal" = optimal, "params" = parms, "heat" = heatr)
# })
# names(ycost) <- croplnms
# clength <- t(sapply(ycost, function(x) c(nrow(x$params), nrow(x$optitab))))

cnames <- c("C", "BD")
bdc <- lapply(crops, function(x) {
  a <- Sys.time()
  print(paste("Starting run for", x, "at", a))
  otab <- pareto(cnames, step = step, prod_targ = targ[x], 
                  yblist = ybl, currprodmod = g[x], input_key = "ZA", 
                  Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
                  Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
                  silent = FALSE, ncl = 7)
  load(fp(p_out, "bcode.rda"))
  # heatr <- heat2(fp(p_out, bcode), basedt, todisk = TRUE) 
  print(Sys.time() - a)
  c("bcode" = bcode, otab, "heat" = heatr)
})
names(bdc) <- croplnms

# fix because ran with heat2 not yet adjusted for improperly ordered csv files
bdcfix <- lapply(bdc, function(x) {  # x <- ycost$both
  if(nrow(x$params) > nrow(x$optitab)) {
    print(paste("fixing heat map for", x$bcode))
    heatfix <- heat2(fp(p_out, x$bcode), basedt, TRUE, TRUE)
  } else {
    heatfix <- NULL
  }
  heatfix
})
for(i in 1:length(bdc)) bdc[[i]]$heat <- bdcfix[[i]]

# plot(bdc$both$optitab$C, bdc$both$optitab$BD)
# bdc3 <- c(bdc, bdc2)  # vestiges to show I forgot to do maize soy case
# bdc <- bdc3

# # Fix pareto tab
# load(fp(fp(p_out, bdc$both$bcode), "impacts_tab.rda"))
# inlist <- lapply(unique(outtab$iter), function(x) outtab[outtab$iter == x, ])
# outtabf <- batch_stat(inlist, Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, 
#                       Yst = Yst, Cst = Cst, BDst = BDst, COSTst = COSTst)

# bdcfix <- lapply(bdc, function(x) {  # x <- bdc$maize
#   if(nrow(x$params) > nrow(x$optitab)) {
#     print(paste("fixing heat map for", x$bcode))
#     heatfix <- heat2(x, fp(p_out, x$bcode), basedt, todisk = TRUE)
#   } else {
#     heatfix <- NULL
#   }
#   heatfix
# })
# for(i in 1:length(bdc)) bdc[[i]]$heat <- bdcfix[[i]]

# bdc <- lapply("ZA_20160215_072332_1558_54465", function(x) {
#   bpath <- fp(p_out, x)
#   load(fp(bpath, "impacts_tab.rda"))
#   inlist <- lapply(unique(outtab$iter), function(x) {
#     outtab[outtab$iter == x, ]
#   })
#   # load(fp(bpath, "optitab.rda"))
#   optimal <- batch_stat(inlist, Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, 
#                         Yst = Yst, Cst = Cst, BDst = BDst, COSTst = COSTst)
#   save(optimal, file = fp(bpath, "optitab.rda"))
#   load(fp(bpath, "parms.rda"))
#   heatr <- heat2(fp(p_out, x), basedt, todisk = TRUE, overwrite = TRUE) 
#   list("bcode" = x, "optimal" = optimal, "params" = parms, "heat" = heatr)
# })
# names(bdc) <- croplnms

# save(cbdc, ycost, bdc, file = fp(p_out, "mainresults1402.rda"))
save(ycost, bdc, file = fp(p_out, "mainresults1702.rda"))
```

# fix because ran with heat2 not yet adjusted for improperly ordered csv files
ybdcfix <- lapply(ybdc, function(x) {  # x <- ycost$both
  if(nrow(x$params) > nrow(x$optitab)) {
    print(paste("fixing heat map for", x$bcode))
    heatfix <- heat2(fp(p_out, x$bcode), basedt, TRUE, TRUE)
  } else {
    heatfix <- NULL
  }
  heatfix
})
for(i in 1:length(ybdc)) ybdc[[i]]$heat <- ybdcfix[[i]]

# ran because of fail on iteration for both (croplnms not properly compiled)
# bnames <- c("ZA_20160213_231906_17404_28678", "ZA_20160213_234959_17404_39818")
# ybdc <- lapply("ZA_20160215_072541_1558_17131", function(x) {
#   bpath <- fp(p_out, x)
#   load(fp(bpath, "impacts_tab.rda"))
#   inlist <- lapply(unique(outtab$iter), function(x) {
#     outtab[outtab$iter == x, ]
#   })
#   # load(fp(bpath, "optitab.rda"))
#   optimal <- batch_stat(inlist, Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, 
#                         Yst = Yst, Cst = Cst, BDst = BDst, COSTst = COSTst)
#   save(optimal, file = fp(bpath, "optitab.rda"))
#   load(fp(bpath, "parms.rda"))
#   heatr <- heat2(fp(p_out, x), basedt, todisk = TRUE, overwrite = TRUE) 
#   list("bcode" = x, "optimal" = optimal, "params" = parms, "heat" = heatr)
# })
# names(ybdc) <- croplnms

# heat maps
# ybdcheat <- lapply(ybdc, function(x) {  # x <- bdc$maize
#   print(paste("N params =", nrow(x$params), ": N optimal =",  nrow(x$optitab)))
#   heatfix <- heat2(x, fp(p_out, x$bcode), basedt, todisk = TRUE, 
#                    overwrite = TRUE)
#   heatfix
# })
# for(i in 1:length(ybdc)) ybdc[[i]]$heat <- ybdcheat[[i]]

# plot(ybdc$maize$heat)
# par(mfrow = c(1, 2))
# plot(ycost$maize$heat)
# plot(ycost$soy$heat)
# plot(ycost$both$heat)
# plot(bdc$both$heat)
# save(ybdc, cbdc, ycost, bdc, file = fp(p_out, "mainresults1502.rda"))
save(ybdc, ycost, bdc, file = fp(p_out, "mainresults1702.rda"))
# load(fp(p_out, "mainresults1402.rda"))
```

## Figures

How reconcilable are the different land use interests, and what would be the impacts of each?

I am using the two crops combined approach because there is little overlap between the two.

### Figure 1
```{r, eval = FALSE}
# select out results for "pure" cases (weight = 1)
pure <- sapply(cnames, function(x) which(round(ybdc$both$params[, x], 4) == 1))

fnames <- imp_sorter(fp(p_out, ybdc$both$bcode), inds = pure, fullnames = TRUE)
pure_r <- lapply(fnames, function(x) {  # x <- pure[1]
  DT <- cbind(fread(x), basedt[, .(x, y, convertible)])
  DTr <- dt_to_raster(DT, CRSobj)
})
# sapply(1:4, function(x) which(ps[, x] == 1))
# sum across crops and multiply by convertible areas
rs <- lapply(pure_r, function(x) calc(x[[1:2]], sum) * x[[3]])  # actual area
rs2 <- lapply(pure_r, function(x) calc(x[[1:2]], sum))  # conv pixels
# check
# sapply(rs, function(x) cellStats(x, sum))
# ybdc$both$optitab[ind %in% pure, Y]  # same, but C optimized out
# sapply(rs2, function(x) cellStats(x, sum))
# plot(pure_r[[3]])

# figure out overlaps between different pure objectives
pms <- expand.grid(rep(list(0:1), 4))[-1, ]  # logic grid
rownames(pms) <- 1:15
rs_over <- lapply(1:nrow(pms), function(x) {  # apply logic tests
  (rs2[[1]] == pms[x, 1]) & (rs2[[2]] == pms[x, 2]) & (rs2[[3]] == pms[x, 3]) &     (rs2[[4]] == pms[x, 4])
})
rs_overs <- stack(rs_over)

# legend to show class of overlap
pms$leg <- c("Y", "C", "YC", "Bd", "YBd", "BdC", "YBdC", "Ct", 
             "YCt", "CCt", "YCCt", "BdCt", "YBdCt", "CBdCt", 
             "YCBdCt")

# frequency of overlaps in different categories
# sum(pms[c(1, 3, 5, 7, 9, 11, 13, 15), "hist"])
pms$hist <- sapply(1:nlayers(rs_overs), function(x) {
  round(cellStats(rs_overs[[x]] * pure_r[[1]]$convertible, sum), 1)
})

# legend color
pms$col <- c("dodgerblue3", "goldenrod2", "tomato1", "yellow", 
             rep("tomato1", 2), "red3", "deepskyblue1", rep("tomato1", 2),
             rep("red3", 5))

# recode with unique number for overlap class, collapse to RasterLayer, 
# simplify classes for plotting
rs_over_rc <- stack(lapply(1:length(rs_over), function(x) rs_over[[x]] * x))
rs_over_rc <- calc(rs_over_rc, sum)
# plot(rs_over_rc == 6)
rclmat <- cbind(0:15, c(0, 1, 3, 5, 4, 5, 5, 6, 2, 5, 5, 6, 5, 6, 6, 6))
leg2 <- c("Yield", "Cost", "Carbon", "Biodiversity", "2 overlap", "3+ overlap")
rs_over_rc2 <- raster::reclassify(rs_over_rc, rclmat)

# plot(1:2, pch = 20, cex = 3, col = c("yellow", "yellow2"))

# For Panel B - impact statistics 
bpath <- fp(p_out, ybdc$both$bcode)
load(fp(bpath, "impacts_tab.rda"))  # get impacts table

# select out corresponding impact statistics, summarize
pure2 <- unlist(lapply(pure, function(x) c(x, x+1)))
vars <- c("iter", "conv_area", "tot_C", "fpa_conv", "mu_cost", "rarity",
          "priority",  "int_prior", "int_mean")
conv_stats <- selected_impacts(pure, fp(p_out, ybdc$both$bcode))
# conv_stats <- outtab[outtab$iter %in% pure, vars]
# conv_stats <- data.frame(t(sapply(pure, function(x) {  # x <- pure[1]
#   DF <- conv_stats[conv_stats$iter == x, ]
#   c(colSums(DF[, 2:4]), 
#     sapply(5:ncol(DF), function(y) weighted.mean(DF[, y], DF$conv_area)))
# }))) 
# colnames(conv_stats) <- vars[-1]

# rescale for common plot
svec <- c(100000, 10000000, 1000, 1, 0.1, 0.1, 0.1, 0.1)  # rescale factor
conv_stats_n <- sweep(as.matrix(conv_stats)[, -1], MARGIN = 2, svec, "/")
conv_stats_n <- conv_stats_n[, c(1, 4, 2, 6:ncol(conv_stats_n), 3)]

# Plots
# Panel A
# cols <- RColorBrewer::brewer.pal(11, "RdYlBu")
# cols <- colorspace::diverge_hsv(n = 11)
# colsi <- sapply(c(0.5, 0.75, 1), function(x) rgb(1, 1, 0.9, alpha = x))
cols <- c("dodgerblue3", "deepskyblue1", "goldenrod2", "yellow", "tomato1",
          "red3")
plot(1:6, pch = 20, cex = 3, col = cols)

tiff(fp(p_figures, "single_priorities.tif"), height = 3, width = 8, 
     units = "in", res = 300)
par(mfrow = c(1, 3))
imp_plot2(dtr = rs_over_rc2, impacts = i1, fpath = p_figures, 
          fnm = "pure_overlap", cexscale = 0.6, ftitle = "", crops = leg2, 
          stats = FALSE, cols = cols, hold = TRUE, marg = c(0, 0, 0, 0))

# Panel B
# totf <- cellStats(rs_over_rc > 0, sum)
par(mar = c(7, 4, 2, 2))
bp <- barplot(pms$hist / sum(pms$hist) * 100, ylim = c(0, 25), las = 2, 
              col = pms$col, mgp = c(2, 0.25, 0), tcl = -0.2, 
              ylab = "% converted area")
axis(side = 1, at = bp, labels = pms$leg, las = 2, mgp = c(2, 0.25, 0), 
     tcl = -0.2)
# TeachingDemos::subplot( 
#   bp <- barplot(pms$hist / sum(pms$hist) * 100, ylim = c(0, 25), las = 2, 
#                 col = pms$col, mgp = c(2, 0.25, 0), tcl = -0.2, 
#                 ylab = "% converted pixels", names.arg = pms$leg), 
#   x=grconvertX(c(0.1,0.45), from='npc'),
#   y=grconvertY(c(0.6,1), from='npc'),
#   type='fig', pars=list(mar=c(3,3,0,0) + 0.1))

# Panel C
# barplot(conv_stats_n)
blabs <- c("Area", "Time", "Carbon", "Priority", "Priority/intactness", 
           "Intactness", "Forest reserves")
# blabs <- sub(':', '\n', blabs)
tlabs <- c(expression(10^5~"km"^2), "hours", expression(10^7~"tons"), 
           rep("X10", 3), expression(10^3~"km"^2))
bp <- barplot(conv_stats_n, beside = TRUE, ylim = c(0, 14), las = 2, 
              col = pms$col[c(1, 2, 4, 8)], names.arg = rep("", length(blabs)), 
              ylab = "Impact*", mgp = c(2, 0.25, 0), tcl = -0.2)
text(x = bp[2, ] - 0.4, y = rep(-0.3, length(bp[1, ])), adj = 1, 
     labels = blabs, xpd = NA, srt = 90)
text(x = bp[3, ] + 0.4, y = rep(-0.3, length(bp[3, ])), adj = 1, 
     labels = tlabs, xpd = NA, srt = 90, cex = 0.8)
dev.off()

#### Need to redo pareto to pass in weighted mean function for all average 
#### costs (DONE)

@@

## Figure 2 & 3 (probably supplemental)
```{r, eval = FALSE}
# yc_bdc_st <- as.matrix(stack(ycost$both$heat, bdc$both$heat) / 100)
# yc_bdc_st <- stack(ycost$both$heat, ycost$both$heat * 0, bdc$both$heat) / 100
# plot(ycost$both$heat > 1)
# plotRGB(yc_bdc_st, r = 1, g = 2, b = 3, colNA = "transparent", scale = 1)
# rgb(red = yc_bdc_st[, 1], rep(0, nrow(yc_bdc_st)), yc_bdc_st[, 2])
# plot(ycost$both$heat)

# individual maps
png(full_path(p_figures, "all-4-maps.png"), height = 7, width = 7, 
     units = "in", res = 300)
par(mfrow = c(2, 2))#, oma = c(0, 0, 0, 2))
ftitles <- c("Yield", "Carbon", "Biodiversity", "Cost")
legp <- c(TRUE, rep(FALSE, 3))
for(i in 1:4) {
  dtr <- calc(pure_r[[i]][[1:2]] * c(1, 2), sum)
  imp_plot2(dtr, impacts = i1, fpath = p_figures, fnm = "all-4-maps", 
            cexscale = 0.6, ftitle = ftitles[i], crops = c("maize", "soy"), 
            stats = FALSE, hold = TRUE, legend = legp[i], marg = c(0, 0, 2, 0))
}
dev.off()

# heat maps
implist <- list(ycost$both, bdc$both)
load(full_path(set_base_path(), paste0("external/data/ZA/parks_roads.rda")))
pacols <- c("transparent", "grey85", "grey75")
png(full_path(p_figures, "ycost-bdc-heat.png"), height = 400, width = 900)
par(mfrow = c(1, 2), oma = c(0, 0, 0, 2))
for(i in 1:2) {
  par(mar = c(1, 1, 1, 4))
  plot(zambia, col = "grey90", border = "transparent")
  ir <- implist[[i]]$heat
  ir[ir == 0] <- NA
  plot(ir, col = rev(heat.colors(20)), add = TRUE, )
  plot(pas[pas@data$type == "gma", ], add = TRUE, col = pacols[2],
       border = FALSE)
  plot(pas[pas@data$type == "npark", ], add = TRUE, col = pacols[3],
       border = FALSE)
  plot(roads, add = TRUE, lwd = 0.1, col = "grey")
}
dev.off()

@@

## Figure 4

Value of just a bit of compromise

```{r, eval = FALSE}
p <- data.frame(ybdc$both$params)
outtab[1, ]
p[, c("Y", "C", "BD" ,"COST")] <- round(p[, c("Y", "C", "BD" ,"COST")], 2)
# scens <- list(c(0.9, 0.05, 0.05, 0), 
#               c(0.85, 0.05, 0.05, 0.05), 
#               c(0.1, 0.45, 0.45, 0.0), 
#               c(0.05, 0.45, 0.45, 0.05))
scens <- lapply(c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9), function(x) {
  c(1 - x, rep(x / 2, 2), 0)
})
# scens <- lapply(c(0, 0.15, 0.3, 0.45, 0.6, 0.75), function(x) {
#   c(1 - x, rep(x / 3, 3))
# })
pind <- sapply(scens, function(x) {
  x <- round(x, 2)
  which(p$Y == x[1] & p$C == x[2] & p$BD == x[3] & p$COST == x[4])
})

# select out impacts corresponding to those runs
cstats <- selected_impacts(pind, p_out, ybdc$both$bcode)

# check on selection
# il <- input_handler(p_moddat, crops[[1]])
# chk <- tradeoff_mod(targ, ybdc$both$params[pind[5], 7:10], 
#                     currprodmod = g, exist_list = il)
# DF <- data.frame(chk$impacts)
# outtab[outtab$iter == pind[5], -2]
# round(c(colSums(DF[, 2:4]),
#         sapply(5:ncol(DF), function(z) weighted.mean(DF[, z], DF$conv_area))), 
#       2)
# cstats[5, ]
outtab[outtab$iter == pind[5], ]
outtab[, 1:4][1:100,]

fnames <- dir(bpath, pattern = "csv")
fnames[pind[5]]

# calculate max impacts across both crops, and figure out the impact range, 
# and what percent that is relative to the worst case
allstats <- selected_impacts(1:nrow(p), p_out, ybdc$both$bcode)
minmaxstats <- allstats[, lapply(.SD, range)]
imp_range <- minmaxstats[, lapply(.SD, diff)]  # difference between best/worst
pct_of_tot <- minmaxstats[, lapply(.SD, function(x) diff(x) / max(x))]

dfunc <- function(x, y) 100 - y / x * 100
stnms <- names(cstats)[-1]
imp_pct <- cstats[, lapply(stnms, function(x) {
  dfunc(minmaxstats[[x]][2], get(x))
})]
setnames(imp_pct, stnms)

plot(imp_pct$tot_C, imp_pct$conv_area, type = "l", xlab = "", ylab = "", 
     axes = FALSE)        # xaxs = "r", yaxs = "r")
